---
title: "Data Cleaning"
author: "Chris"
date: "2025-01-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import our Data

First we pull in the spreadsheet.
```{r import}
library(readxl)
data <- read_excel("data/Rainydawg_top_music_of_2024_Survey.xlsx")
## What are we looking at here, let's summary()
#summary(data)

library(tidyr)
library(dplyr)
#Here we drop the first row, it's a placeholder
data <- data[-1, ]

# create a new empty, list() for all our entries
entries_list <- list()

#Fix our columns, we want unique names and no spaces. Plug it in.
new_column_names <- c("Timestamp", "Email", "Name", "Role", "Rank01", "Rank02", "Rank03", "Rank04", "Rank05", "Rank06", "Rank07", "Rank08", "Rank09", "Rank10", "Rank11", "Rank12", "Rank13", "Rank14", "Rank15", "Rank16", "Rank 17", "Rank18", "Rank19", "Rank20", "Rank21", "Extra", "Notes")
colnames(data) <- new_column_names
data
```

## Make it Clean
Now we look at the first list...need to pull our artist and title into separate columns.
```{r List by Count}

## We only care about the entries at this point. DJ and
##names can be useful later.
## Keep only the columns that contain artist-title pairs.
## also remove the Rank21 column. The original proposition was was top 20,
## I made an error on the input form, and added an extra row.
data <- data %>% select(-Timestamp, 
                    -Email,
                    -Name,
                    -Role,
                    -Rank21, 
                    -Extra,
                    -Notes)

# take each column, separate them into two columns for artist and title, 
# and trim the whitespace and save into entries_list()
for (column in names(data)) {
  temp_df <- data.frame(Column = data[[column]])
  temp_entries <- temp_df %>% 
    separate(col = Column, into = c("Artist", "Title"), sep = "-+", remove = TRUE) %>% 
    mutate(across(c(Artist, Title), trimws))
  entries_list[[length(entries_list) + 1]] <- temp_entries
}

# Loop through the list of dataframes
for (i in 1:length(entries_list)) {
  # Calculate the weight value based on the position in the list
  weight_value <- 1 / i
  
  # Add a new column 'weight' to the current dataframe
  entries_list[[i]]$weight <- rep(weight_value, nrow(entries_list[[i]]))
}


#Create a new list for sorting popular count
countedEntriesList <- bind_rows(entries_list)
## you need to catch this title bc it was input incorrectly
countedEntriesList$Title <- gsub("I LAY MY LIFE DOWN FOR YOU", "I LAY DOWN MY LIFE FOR YOU", countedEntriesList$Title)

#Drop any rows that are incomplete
countedEntriesList <- drop_na(countedEntriesList) 
#Put the artist into lowercase for all entries
countedEntriesList$ArtisttoLowercase <- tolower(countedEntriesList$Artist)
#Put the title into lowercase for all entries
countedEntriesList$TitletoLowercase <- tolower(countedEntriesList$Title)

library(stringr)
countedEntriesList$TitletoLowercase <- str_replace_all(countedEntriesList$TitletoLowercase, "&", "and")
countedEntriesList$TitletoLowercase <- str_remove_all(countedEntriesList$TitletoLowercase, "[[:punct:]]")
countedEntriesList$ArtisttoLowercase <- iconv(countedEntriesList$ArtisttoLowercase, from = "UTF-8", to = "ASCII//TRANSLIT")
countedEntriesList$ArtisttoLowercase <- str_remove_all(countedEntriesList$ArtisttoLowercase, "[[:punct:]]")
## Q1: do we count brat and brat remix as the same release?
countedEntriesList$TitletoLowercase <- gsub("brat and its completely different but also still brat", "brat", countedEntriesList$TitletoLowercase)
countedEntriesList


```
We use stringdist below, to make a comparison of the artist name against the vector,
ask it to be within a threshold of 2 differences.
```{r}
# Install and load the stringdist package
##install.packages("stringdist")
library(stringdist)

# Create a copy of countedReleasesList
ArtistsList <- countedEntriesList

unique_artists <- unique(countedEntriesList$ArtisttoLowercase)
# Iterate through ArtistsList
for (i in 1:nrow(ArtistsList)) {
  artist <- ArtistsList$ArtisttoLowercase[i]
  similar_artists <- unique_artists[stringdist(artist, unique_artists) <= 1]
  ArtistsList$Count[i] <- sum(ArtistsList$ArtisttoLowercase %in% similar_artists)
}

# Count occurrences of each artist name and deduplicate
countedArtistsList <- ArtistsList %>% 
  group_by(Artist) %>% 
  summarise(Count = n()) 
ArtistsList
#Save our list of artists and count of appearances. Need to manually check this before
#using it later.
# Install and load the writexl package
#install.packages("writexl")
library(writexl)
write_xlsx(ArtistsList, "output/countedArtistsList.xlsx")
# NOTE:
# you still have to clean this, the Waxahatchee ft MJL will get missed.

```
Then we do a similar thing for our Releases, and we go back to our entries.

```{r}
# Create a copy of countedReleasesList

countedReleasesList <- countedEntriesList
countedReleasesList$CountOfMentions <- sapply(seq_along(countedReleasesList$TitletoLowercase), function(i) sum(stringdist::stringdist(countedReleasesList$TitletoLowercase[i], countedReleasesList$TitletoLowercase) <= 1))
countedReleasesList 
#Save our list of releases and count of appearances. Need to manually check this before
#using it later.
write_xlsx(countedReleasesList, "output/countedReleasesList.xlsx")
```
Creating a weighted list
```{r}
 

#Create a new list for sorting popular count
weightedReleasesList <- countedEntriesList

df <- weightedReleasesList %>% 
  group_by(TitletoLowercase) %>% 
  mutate(sum = sum(weight)) %>% 
  ungroup()

write_xlsx(df, "output/weightedReleasesList.xlsx")
```

