---
title: "1_tables"
author: "chris"
date: "2025-02-01"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Intro

Number of Lists included: 12
provided by: Rainydawg DJs, Blawg Team, and Volunteers
```{r}
#install.packages("openxlsx")
library(openxlsx)
library(dplyr)

# Load required data from output files
weightedReleasesList <- read.xlsx("output/weightedReleasesList.xlsx")
countedReleasesList <- read.xlsx("output/countedReleasesList.xlsx")
df <- read.xlsx("output/weightedReleasesList.xlsx")

print.data.frame(djNames)
```


## Top Releases by RainyDawg #1 Votes

Everybody's favorite contribution from 2024, alphabetical by Title:

```{r}
print.data.frame(countedReleasesList %>%
                   select(Artist, Title, borda_score, TitletoLowercase) %>%
                   filter(borda_score == 20) %>%
                   arrange(TitletoLowercase))
# Write the dataframe to an Excel file
write.xlsx(countedReleasesList %>%
             select(Artist, Title, borda_score, TitletoLowercase) %>%
             filter(borda_score == 20) %>%
             arrange(TitletoLowercase), "output/TopReleasesByNum1Votes.xlsx")
```

## Top Releases

Weighted by Borda Count:
The borda_sum column shows the aggregated score. For each ranking, I calculated the Borda score
as: (max_rank + 1) - rank. With 20 ranking positions, a #1 vote = 20 points, #2 = 19 points,
..., #20 = 1 point. This provides a more linear weighting than the fractional method.
```{r pressure, echo=FALSE}
library(dplyr)
print.data.frame(df %>%
                   select(Artist, Title, borda_sum, TitletoLowercase) %>%
                   distinct(TitletoLowercase, .keep_all = TRUE) %>%
                   arrange(desc(borda_sum)))
write.xlsx(df %>%
             select(Artist, Title, borda_sum, TitletoLowercase) %>%
                   distinct(TitletoLowercase, .keep_all = TRUE) %>%
                   arrange(desc(borda_sum)), "output/TopReleases.xlsx", rowNames = TRUE)
```

## Top Releases by Exponential Decay

Weighted by Exponential Decay:
After the initial rapid drop, the penalty rate slows down. This ensures that while new items are
prioritized, old but highly relevant items are not completely eliminated from results. The
decay factor of 0.85 will decrease the importance rapidly at first, but then more slowly.

```{r, echo=FALSE}
print.data.frame(df %>%
                   select(Artist, Title, exponential_decay_sum, TitletoLowercase) %>%
                   distinct(TitletoLowercase, .keep_all = TRUE) %>%
                   arrange(desc(exponential_decay_sum)))
write.xlsx(df %>%
             select(Artist, Title, exponential_decay_sum, TitletoLowercase) %>%
                   distinct(TitletoLowercase, .keep_all = TRUE) %>%
                   arrange(desc(exponential_decay_sum)),
           "output/TopReleasesbyExponentialDecay.xlsx", rowNames = TRUE)
```

## Top Releases by Inclusion

Just by mentions

```{r, echo=FALSE}
print.data.frame(countedReleasesList %>% 
                   select(Artist, Title, CountOfMentions, TitletoLowercase) %>% 
                   distinct(TitletoLowercase, .keep_all = TRUE) %>% 
                   arrange(desc(CountOfMentions), TitletoLowercase))
write.xlsx(countedReleasesList %>%
             select(Artist, Title, CountOfMentions, TitletoLowercase) %>% 
             distinct(TitletoLowercase, .keep_all = TRUE) %>% 
             arrange(desc(CountOfMentions), TitletoLowercase),
           "output/TopReleasesbyInclusion.xlsx", rowNames = TRUE)
```

<!-- ## Top Artists -->

<!-- ## Top Artists by Inclusion -->

<!-- Artists by mentions -->

<!-- ```{r, echo=FALSE} -->
<!-- print.data.frame(ArtistsList %>%  -->
<!--                    select(Artist, Count, ArtisttoLowercase) %>%  -->
<!--                    distinct(ArtisttoLowercase, .keep_all = TRUE) %>%  -->
<!--                    arrange(desc(Count), ArtisttoLowercase)) -->

<!-- ``` -->


## Unique Releases

These are the 103 unique releases as entered by RainyDawg
```{r}
print.data.frame(weightedReleasesList %>% 
                   distinct(TitletoLowercase, .keep_all = TRUE) %>%
                   select(Artist, Title, TitletoLowercase) %>% 
                   arrange(TitletoLowercase))
write.xlsx(weightedReleasesList %>%
             distinct(TitletoLowercase, .keep_all = TRUE) %>%
             select(Artist, Title, TitletoLowercase) %>% 
             arrange(TitletoLowercase),
           "output/UniqueReleases.xlsx", rowNames = TRUE)
```


