---
title: "1_tables"
author: "chris"
date: "2025-02-01"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Intro

Number of Lists included: 12
provided by:
```{r}
print.data.frame(djNames)
```


## Top Releases by DJ #1 Votes
```{r}
print.data.frame(countedReleasesList %>%
                   select(Artist, Title, weight, TitletoLowercase) %>% 
                   filter(weight == 1) %>% 
                   arrange(TitletoLowercase))

```

## Top Releases

Weighted by rank:
The number in the sum column is there for math, just pay attention to the list
from top to bottom. For the ranking of each release, I calculated the weight as a fraction. The 
numerator is always 1, and the denominator is the rank that the DJ assigned it. 
E.g., a rank of #1 would be a weight of 1, a rank of #5 would be a weight of 1/5, or 0.2.
```{r pressure, echo=FALSE}
library(dplyr)
print.data.frame(df %>% 
                   select(Artist, Title, sum, TitletoLowercase) %>% 
                   distinct(TitletoLowercase, .keep_all = TRUE) %>% 
                   arrange(desc(sum)))

```


## Top Releases by Inclusion

Just by mentions

```{r, echo=FALSE}
print.data.frame(countedReleasesList %>% 
                   select(Artist, Title, CountOfMentions, TitletoLowercase) %>% 
                   distinct(TitletoLowercase, .keep_all = TRUE) %>% 
                   arrange(desc(CountOfMentions), TitletoLowercase))

```

## Top Artists

## Top Artists by Inclusion

Artists by mentions

```{r, echo=FALSE}
print.data.frame(ArtistsList %>% 
                   select(Artist, Count, ArtisttoLowercase) %>% 
                   distinct(ArtisttoLowercase, .keep_all = TRUE) %>% 
                   arrange(desc(Count), ArtisttoLowercase))

```


## Unique Releases
```{r}
print.data.frame(weightedReleasesList %>% 
                   distinct(TitletoLowercase, .keep_all = TRUE) %>%
                   select(Artist, Title, TitletoLowercase) %>% 
                   arrange(TitletoLowercase))
```


