---
title: "1_tables"
author: "chris"
date: "2025-02-01"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Intro

Number of Lists included: 12
provided by: Rainydawg DJs, Blawg Team, and Volunteers
```{r}
#install.packages("openxlsx")
library(openxlsx)
print.data.frame(djNames)
```


## Top Releases by RainyDawg #1 Votes

Everybody's favorite contribution from 2024, alphabetical by Title:

```{r}
print.data.frame(countedReleasesList %>%
                   select(Artist, Title, weight, TitletoLowercase) %>% 
                   filter(weight == 1) %>% 
                   arrange(TitletoLowercase))
# Write the dataframe to an Excel file
write.xlsx(countedReleasesList %>%
             select(Artist, Title, weight, TitletoLowercase) %>% 
             filter(weight == 1) %>% 
             arrange(TitletoLowercase), "output/TopReleasesByNum1Votes.xlsx")
```

## Top Releases

Weighted by rank:
The number in the sum column is there for math, just pay attention to the list
from top to bottom. For the ranking of each release, I calculated the weight as a fraction. The 
numerator is always 1, and the denominator is the rank that the contributor assigned it. 
E.g., a rank of #1 would be a weight of 1, a rank of #5 would be a weight of 1/5, or 0.2.
```{r pressure, echo=FALSE}
library(dplyr)
print.data.frame(df %>% 
                   select(Artist, Title, sum, TitletoLowercase) %>% 
                   distinct(TitletoLowercase, .keep_all = TRUE) %>% 
                   arrange(desc(sum)))
write.xlsx(df %>%
             select(Artist, Title, sum, TitletoLowercase) %>% 
                   distinct(TitletoLowercase, .keep_all = TRUE) %>% 
                   arrange(desc(sum)), "output/TopReleases.xlsx", rowNames = TRUE)
```


## Top Releases by Inclusion

Just by mentions

```{r, echo=FALSE}
print.data.frame(countedReleasesList %>% 
                   select(Artist, Title, CountOfMentions, TitletoLowercase) %>% 
                   distinct(TitletoLowercase, .keep_all = TRUE) %>% 
                   arrange(desc(CountOfMentions), TitletoLowercase))
write.xlsx(countedReleasesList %>%
             select(Artist, Title, CountOfMentions, TitletoLowercase) %>% 
             distinct(TitletoLowercase, .keep_all = TRUE) %>% 
             arrange(desc(CountOfMentions), TitletoLowercase),
           "output/TopReleasesbyInclusion.xlsx", rowNames = TRUE)
```

<!-- ## Top Artists -->

<!-- ## Top Artists by Inclusion -->

<!-- Artists by mentions -->

<!-- ```{r, echo=FALSE} -->
<!-- print.data.frame(ArtistsList %>%  -->
<!--                    select(Artist, Count, ArtisttoLowercase) %>%  -->
<!--                    distinct(ArtisttoLowercase, .keep_all = TRUE) %>%  -->
<!--                    arrange(desc(Count), ArtisttoLowercase)) -->

<!-- ``` -->


## Unique Releases

These are the 103 unique releases as entered by RainyDawg
```{r}
print.data.frame(weightedReleasesList %>% 
                   distinct(TitletoLowercase, .keep_all = TRUE) %>%
                   select(Artist, Title, TitletoLowercase) %>% 
                   arrange(TitletoLowercase))
write.xlsx(weightedReleasesList %>%
             distinct(TitletoLowercase, .keep_all = TRUE) %>%
             select(Artist, Title, TitletoLowercase) %>% 
             arrange(TitletoLowercase),
           "output/UniqueReleases.xlsx", rowNames = TRUE)
```


